{\bf Stateless Model Checking \\ with Data-Race Preemption Points}

### 2016-03-01 oopsla/calcm.tex
small edits calcm

\begin{frame}{The Happens-Before (HB) Relation}
	Most data-race analyses use {\em Pure HB} to determine simultaneity.
	\begin{itemize}
		\item HB is established by any synchronization (mutexes, cvars, xchg...)
		\item Represents possiblity to threads' behaviour to change if reordered
			%\begin{itemize}
			%	\item ...that the programmers obviously intended.
			%\end{itemize}
		\item May exclude some races from alternate interleavings ({\em false negatives})
	\end{itemize}
	\pause
	\linegap

	To avoid false negatives, we use {\em Limited HB}\related{O'Callahan '03} instead.
	%, Serebryany '09}
	\begin{itemize}
		\item HB is established only when thread runnability changes (cvars).
		\item Represents possibility to reorder accesses to occur simultaneously
		\item Captures accesses separated by unrelated, synchronized, logic
		\item Will also falsely flag some {\em false positives}
		\item Combined with lock-set analysis to increase accuracy
	\end{itemize}
\end{frame}

@@

	Synchronization API PPs \& data-race PPs are sufficient!
	\begin{itemize}
		\item {\bf Theorem (Convergence)}:
			{\em If a bug can be exposed by any thread interleaving
				possible by preempting on all instructions,
				% during a specific test
			Quicksand will eventually test an equivalent interleaving which exposes the same bug.}
		\item Proof appeals to DPOR soundness\related{Flanagan '05} and Limited HB.
	\end{itemize}
\end{frame}

>>>>

\begin{frame}{The Happens-Before (HB) Relation}
	Most data-race analyses use {\em Pure HB} to determine simultaneity.
	\begin{itemize}
		\item HB is established by any synchronization (mutexes, cvars, xchg...)
		\item Represents possiblity of threads' behaviour to change if reordered
			%\begin{itemize}
			%	\item ...that the programmers obviously intended.
			%\end{itemize}
		\item May exclude some races from alternate interleavings ({\em false negatives})
	\end{itemize}
	\pause
	\linegap

	To avoid false negatives, we use {\em Limited HB}\related{O'Callahan '03} instead.
	%, Serebryany '09}
	\begin{itemize}
		\item HB is established only when thread runnability changes (cvars).
		\item Represents ability to reorder accesses to occur simultaneously
		\item Captures accesses separated by unrelated, synchronized, logic
		\item Will also falsely flag some {\em false positives}
		\item Combined with lock-set analysis to increase accuracy
	\end{itemize}
\end{frame}

@@

	Synchronization API PPs \& data-race PPs are sufficient!
	\begin{itemize}
		\item {\bf Theorem (Convergence)}:
			{\em If a bug can be exposed by any thread interleaving
				possible by preempting on all instructions,
				% during a specific test
			Quicksand will eventually test an equivalent interleaving which exposes the same bug.}
		\item Proof appeals to DPOR soundness\related{Flanagan '05} and Limited HB.
		\item Intuition: ``Adding data-race PPs until saturation = all possible thread communication points.''
	\end{itemize}
\end{frame}
